Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-14 write-ups/PLDI/paper.tex
Shortening.
Minor edits on section 5

The programming model and associated language constructs were inspired
by the requirements of the irregular GPU algorithms proposed in the
literature.  For these algorithms, it was usually easy to identify
where to place the constructs.

@@

\paragraph{Experimental setup}
Cooperative scheduling primitives entails an overhead even if no
killing, forking or resizing never happens. We measure this overhead
via the execution time slowdown between the original kernel and the
cooperative one, forcing the scheduler to never modify the number of
active workgroups. Since the cooperative kernel contains the
non-cooperative kernel code anyway, its occupancy bound may be less
than the original kernel; we make sure to use this occupancy bound as
the number of workgroups for the original kernel in order to compare
relevant execution times. \HEComment{Do we need to mention the
  possible occupancy reduction as an overhead?}

\paragraph{Results}
\mytab~\ref{tab:overhead} lists both geometric mean and maximum value
of measured slowdowns. The overhead is below a 2 times slowdown even
in the worst case, and quite light in general. We consider these
results as encouraging, given that our SVM-based scheduler performance
is likely a far upper bound of what a scheduler implemented directly
in the runtime could offer.

>>>>

@@

\paragraph{Experimental setup}
Cooperative scheduling primitives entails an overhead even if no
killing, forking or resizing happen. We measure this overhead via the
execution time slowdown between the original kernel and the
cooperative one, forcing the scheduler to never modify the number of
active workgroups. Since the cooperative kernel contains the
non-cooperative kernel code anyway, its occupancy bound may be less
than the original kernel; we make sure to use this occupancy bound as
the number of workgroups for the original kernel in order to compare
relevant execution times. \HEComment{Do we need to mention the
  possible occupancy reduction as an overhead?}

\paragraph{Results}
\mytab~\ref{tab:overhead} lists both geometric mean and maximum value
of measured overheads. The slowdown is below 2 even in the worst case,
and closer to 1 in general. We consider these results as encouraging,
especially since our prototype performance is likely a far upper bound
of what a scheduler implemented directly in the runtime could achieve.
